treats manual

### 2023-12-13 inst/gitbook/01_getting_started.Rmd
Updated crude.bd.est with new calculations options

```{r}
## Extracting the crude parameters
(est_params <- crude.bd.est(BeckLee_tree))
## These parameters are the observed speciation and extinction rate per million years.

>>>>

```{r}
## Extracting the crude parameters
(est_params <- crude.bd.est(BeckLee_tree, method = "count"))
## These parameters are the observed speciation and extinction rate per million years.

### 2023-12-13 inst/gitbook/_book/treats_manual.tex
Updated crude.bd.est with new calculations options

\title{treats manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-12-06}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#\# Extracting the crude parameters}
\NormalTok{(est\_params \textless{}{-}}\StringTok{ }\KeywordTok{crude.bd.est}\NormalTok{(BeckLee\_tree))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  ---- treats birth-death parameters object ---- 
## speciation: 0.352.
## extinction: 0.288.
\end{verbatim}

@@

\begin{verbatim}
## Building the tree:....Done.
## Building the tree:.......Done.
## Building the tree:...Done.
## Building the tree:......Done.
## Building the tree:..Done.
## Building the tree:..Done.
## Building the tree:.Done.
## Building the tree:........Done.
## Building the tree:..Done.
## Building the tree:.....Done.
## Building the tree:....Done.
## Building the tree:....Done.
## Building the tree:..Done.
## Building the tree:.................Done.
## Building the tree:....Done.
## Building the tree:....Done.
## Building the tree:..Done.
## Building the tree:......Done.
## Building the tree:.......Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:..Done.
## Building the tree:......Done.
## Building the tree:...........Done.
## Building the tree:......Done.
## Building the tree:....Done.
## Building the tree:.Done.
## Building the tree:..................Done.
## Building the tree:....Done.
## Building the tree:...............Done.
## Building the tree:....Done.
## Building the tree:..Done.
## Building the tree:........Done.
## Building the tree:....Done.
## Building the tree:........Done.
## Building the tree:...Done.
## Building the tree:...Done.
## Building the tree:.Done.
## Building the tree:...Done.
## Building the tree:..............Done.
## Building the tree:...Done.
## Building the tree:.Done.
## Building the tree:..Done.
## Building the tree:....Done.
## Building the tree:..Done.
## Building the tree:..Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:....Done.
## Building the tree:..........Done.
\end{verbatim}

@@

\begin{verbatim}
## Building the tree:.....................Done.
## Building the tree:...................Done.
## Building the tree:.....Done.
## Building the tree:.Done.
## Building the tree:....Done.
## Building the tree:..Done.
## Building the tree:..Done.
## Building the tree:......................Done.
## Building the tree:..Done.
## Building the tree:..Done.
## Building the tree:...Done.
## Building the tree:.Done.
## Building the tree:..Done.
## Building the tree:......Done.
## Building the tree:.Done.
## Building the tree:......Done.
## Building the tree:..Done.
## Building the tree:.Done.
## Building the tree:....Done.
## Building the tree:...Done.
## Building the tree:..Done.
## Building the tree:......Done.
## Building the tree:....................Done.
## Building the tree:...Done.
## Building the tree:.........Done.
## Building the tree:.Done.
## Building the tree:...Done.
## Building the tree:.Done.
## Building the tree:.........Done.
## Building the tree:.Done.
## Building the tree:.............Done.
## Building the tree:..............Done.
## Building the tree:......Done.
## Building the tree:.Done.
## Building the tree:.......Done.
## Building the tree:...Done.
## Building the tree:..Done.
## Building the tree:......Done.
## Building the tree:.Done.
## Building the tree:..Done.
## Building the tree:............Done.
## Building the tree:.....Done.
## Building the tree:......Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:..............Done.
## Building the tree:........Done.
## Building the tree:..............Done.
## Building the tree:.Done.
## Building the tree:..Done.
\end{verbatim}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x55e979290a30>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55e977cfc060>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55e977d04410>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) <= (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55e977d03ae0>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f6e0175d3}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f7aec27f9}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f5c6b6ac6}

>>>>

\title{treats manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-12-13}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#\# Extracting the crude parameters}
\NormalTok{(est\_params \textless{}{-}}\StringTok{ }\KeywordTok{crude.bd.est}\NormalTok{(BeckLee\_tree, }\DataTypeTok{method =} \StringTok{"count"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  ---- treats birth-death parameters object ---- 
## speciation: 0.028.
## extinction: 0.027.
\end{verbatim}

@@

\begin{verbatim}
## Building the tree:....................Done.
## Building the tree:....Done.
## Building the tree:...........Done.
## Building the tree:.Done.
## Building the tree:............Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:..............Done.
## Building the tree:...................................Done.
## Building the tree:......................Done.
## Building the tree:........Done.
## Building the tree:...................Done.
## Building the tree:...Done.
## Building the tree:.......Done.
## Building the tree:.....Done.
## Building the tree:....................Done.
## Building the tree:.Done.
## Building the tree:...Done.
## Building the tree:................Done.
## Building the tree:.......Done.
## Building the tree:.................Done.
## Building the tree:.....Done.
## Building the tree:.................Done.
## Building the tree:............Done.
## Building the tree:....Done.
## Building the tree:....Done.
## Building the tree:...Done.
## Building the tree:...................................................Done.
## Building the tree:...............Done.
## Building the tree:....Done.
## Building the tree:.........Done.
## Building the tree:..................................Done.
## Building the tree:.....Done.
## Building the tree:........Done.
## Building the tree:....Done.
## Building the tree:.Done.
## Building the tree:...................Done.
## Building the tree:...........Done.
## Building the tree:...........Done.
## Building the tree:...........Done.
## Building the tree:.Done.
## Building the tree:...........Done.
## Building the tree:.Done.
## Building the tree:.............Done.
## Building the tree:.............Done.
## Building the tree:........Done.
## Building the tree:.............Done.
## Building the tree:...Done.
## Building the tree:.Done.
\end{verbatim}

@@

\begin{verbatim}
## Building the tree:......................Done.
## Building the tree:...Done.
## Building the tree:..................Done.
## Building the tree:.......Done.
## Building the tree:.................Done.
## Building the tree:...Done.
## Building the tree:..................Done.
## Building the tree:....................Done.
## Building the tree:.Done.
## Building the tree:............Done.
## Building the tree:.Done.
## Building the tree:.Done.
## Building the tree:......Done.
## Building the tree:...............Done.
## Building the tree:....Done.
## Building the tree:.................Done.
## Building the tree:.........Done.
## Building the tree:....Done.
## Building the tree:.....Done.
## Building the tree:....Done.
## Building the tree:......Done.
## Building the tree:.....................Done.
## Building the tree:.................Done.
## Building the tree:.Done.
## Building the tree:....Done.
## Building the tree:...Done.
## Building the tree:...........................Done.
## Building the tree:.......Done.
## Building the tree:.......Done.
## Building the tree:.....Done.
## Building the tree:......Done.
## Building the tree:.......Done.
## Building the tree:.........Done.
## Building the tree:.....Done.
## Building the tree:...Done.
## Building the tree:...................Done.
## Building the tree:............Done.
## Building the tree:......................Done.
## Building the tree:......Done.
## Building the tree:............Done.
## Building the tree:.............Done.
## Building the tree:...........Done.
## Building the tree:..Done.
## Building the tree:.........................Done.
## Building the tree:.Done.
## Building the tree:......................Done.
## Building the tree:.............Done.
## Building the tree:...Done.
## Building the tree:...............Done.
## Building the tree:..........Done.
\end{verbatim}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x560fcf695180>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x560fce0ebbe0>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x560fce0eaf30>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) <= (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x560fce0ea600>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/Rtmp6UK3fU/file52c0514edd4f}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/Rtmp6UK3fU/file52c079e156e9}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/Rtmp6UK3fU/file52c02397d39c}
